---
title: "Introduction to Altmetric"
author: "Karthik Ram"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is a short vignette explaning how to use `rAltmetric`. Altmetric is a private company that collects metrics that go far beyond traditional citations. It collects mentions on various social media to provide a more complete picture of the impact of a scholarly publication. 

The core functionality of the package is captured in two functions:

`altmetrics` - Returns data for a valid identifier such as an altmetric object id, a pubmed ID, an arxiv identifier, a doi, ISBN and so on.  
`altmetric_data` - takes the output of the previous function and returns a tidy data.frame

The package can be used to parse a whole batch of identifiers at once.

e.g.

```{r}
library(rAltmetric)
library(magrittr)
library(purrr)


ids <- list(c(
  "10.1038/nature09210",
  "10.1126/science.1187820",
  "10.1016/j.tree.2011.01.009",
  "10.1086/664183"
))

alm <- function(x)  altmetrics(doi = x) %>% altmetric_data()

results <- pmap_df(ids, alm)
# This results in a data.frame with one row per identifier.
```

You can now see some citation data for these papers.

```{r}
library(dplyr)
knitr::kable(results %>% select(title, doi,  starts_with("cited")))
```

